A Graph Theory Based Approach to MDAO Problem Formulation

### 2013-03-22 graph_syntax.tex
added a graph for constraints and objectives

\begin{figure}[htb!]
  \begin{center}
    \includegraphics[width=.6\textwidth]{images/design_vars_graph}
  \end{center}
  \caption{Simple notional problem with two potential design variables \label{f:design vars}}
\end{figure}

@@

For the proposed syntax, objectives and constraints are represented through the use of 
expression nodes. These nodes contain the actual mathematical expression used to define the 
objective or constraint value. Objective or constraint nodes are distinguished
via the presence of a simple expression (objective) vs an inequality/equality (constraint). 
Fig. [insert ref] shows the notional problem graph augmented with objective and 
constraint values.

[[INSERT ANOTHER GRAPH HERE]]

\begin{comment}
The MDO problem formulation concepts represented by nodes are given in 
Table \ref{t:node representation}, and the concepts represented by edges are 
given in Table \ref{t:edge representation}.
% \begin{itemize}
% \item An objective or constraint is indicated by a variable node with no outgoing edges and with the incoming edges being directed from only other variable nodes.
% \item A global input is a variable node with no edges directed in and with at least two edges directed out to different variable nodes.
% \item A design variable is represented by a variable node with no edges directed in and on fixed edge directed out.
% \end{itemize}
\begin{table}[h!]
 \begin{center}
  \caption{Problem formulation concept represented by a node}
  \label{t:node representation}
  \begin{tabular}{ccc} \hline 
edges directed in & edges directed out & node representation \\ \hline
only explicit edges & none & objective or constraint\\
none & at least two explicit edges & global input \\
none & one fixed edge & design variable \\ \hline
  \end{tabular}
 \end{center}
 \vspace{-15pt}
\end{table}
\begin{table}[h!]
 \begin{center}
  \caption{Problem formulation concept represented by an edge}
  \label{t:edge representation}
  \begin{tabular}{ccc} \hline 
from node & to node & edge representation \\ \hline
variable & variable & connection/passing of a variable\\
variable & model & local input \\
model & variable & local output \\
model & model & function call \\ \hline
  \end{tabular}
 \end{center}
 \vspace{-15pt}
\end{table}
%`Connection' edges connect the local outputs from one analysis block to input nodes.
\end{comment}
\subsection{Local vs Global Nodes}

>>>>

\begin{figure}[htb!]
  \begin{center}
    \includegraphics[width=.6\textwidth]{images/design_vars_graph}
  \end{center}
  \caption{Notional graph with two potential design variables \label{f:design vars}}
\end{figure}

@@

For the proposed syntax, objectives and constraints are represented through the use of 
expression nodes. These nodes contain the actual mathematical expression used to define the 
objective or constraint value. Objective or constraint nodes are distinguished
via the presence of a simple expression (objective) vs an inequality/equality (constraint). 
Fig. \ref{f:obj-cons} shows the notional problem graph augmented with objective and 
constraint values.

\begin{figure}[htb!]
  \begin{center}
    \includegraphics[width=.6\textwidth]{images/obj_const_graph}
  \end{center}
  \caption{Notional graph with and objective and constraint nodes \label{f:obj-cons}}
\end{figure}

\begin{comment}
The MDO problem formulation concepts represented by nodes are given in 
Table \ref{t:node representation}, and the concepts represented by edges are 
given in Table \ref{t:edge representation}.
% \begin{itemize}
% \item An objective or constraint is indicated by a variable node with no outgoing edges and with the incoming edges being directed from only other variable nodes.
% \item A global input is a variable node with no edges directed in and with at least two edges directed out to different variable nodes.
% \item A design variable is represented by a variable node with no edges directed in and on fixed edge directed out.
% \end{itemize}
\begin{table}[h!]
 \begin{center}
  \caption{Problem formulation concept represented by a node}
  \label{t:node representation}
  \begin{tabular}{ccc} \hline 
edges directed in & edges directed out & node representation \\ \hline
only explicit edges & none & objective or constraint\\
none & at least two explicit edges & global input \\
none & one fixed edge & design variable \\ \hline
  \end{tabular}
 \end{center}
 \vspace{-15pt}
\end{table}
\begin{table}[h!]
 \begin{center}
  \caption{Problem formulation concept represented by an edge}
  \label{t:edge representation}
  \begin{tabular}{ccc} \hline 
from node & to node & edge representation \\ \hline
variable & variable & connection/passing of a variable\\
variable & model & local input \\
model & variable & local output \\
model & model & function call \\ \hline
  \end{tabular}
 \end{center}
 \vspace{-15pt}
\end{table}
%`Connection' edges connect the local outputs from one analysis block to input nodes.
\end{comment}

\subsection{Local vs Global Nodes}
